% this is a document answering questions 5 & 6 in Problem Set 1 in Econ5253
\documentclass[12pt]{article}
\begin{document}
\section*{Interest and Reasons for Taking Course}
I am excited to take this Data Science course because I think it will greatly expand not just my technical skills but the scope of research questions I will feel capable of investigating, since increased data allows us to answer more complex questions. I was highly encouraged by previous BA/MA students to take this course because of the broad swath of skills this class teaches and I hope to thoroughly understand them and actively use the tools I've learned (for example, using GitHub to house my thesis information). I am brainstorming what I want to do for my project, but I am not quite sure yet; ideally, I want to do work that is a bit more complex data-wise than pulling data from public datasets as I've done for my economic research. I will probably end up developing some regression analysis. 

My interest in Economics initially stemmed from a desire to have an "employable" degree and has expanded greatly as I've come to appreciate the power of econometrics and social science research. I have many different interests, research-wise (somewhat unfortunately; I fear this leads to me being wide and shallow in a variety of topics) and I have conducted research related to homelessness, politically-induced migration in the US, and finally for my Master's thesis I am investigating the impacts of private school choice policies (such as vouchers) on the revenue of private schools. Broadly, my interests are in education and social interventions/policies (i.e., nonprofit work and policy evaluation). 

I am in the process of finishing graduate school applications. I am applying to programs in social data science, policy evaluation, and public policy analysis. I am basically only applying to competitive programs, though, so after I finish applying I will also apply to jobs. 

\section*{Equation}
$a^2 + b^2 = c^2$
\end{document}